---
title: "Drug misuse in Scotland"
subtitle: "A public health challenge"
author: 'Rosalyn Pearson <br>'
date: "26th October 2022"
output:
  ioslides_presentation:
    css: my-theme.css
---

```{r setup, include = FALSE}
# Load packages required
library(knitr)
library(magrittr)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE)

# Create data frame for table
table_contents <- data.frame(c("Text", "Text",
                               "Text", "Text",
                               "Text"),
                             c(1:5))
```

## Background

- Scotland (as of 2019) has the highest drug deaths rate in Europe, according to the [NRS reporting from European Monitoring Centre for Drugs and Drug Addiction](https://webarchive.nrscotland.gov.uk/web/20210317072542/https://www.nrscotland.gov.uk/files//statistics/drug-related-deaths/2019/drug-related-deaths-19-pub.pdf) - 3.5 times that of the UK
- The rate has also been increasing in recent years
- Important to understand regional and demographic trends as well as trends in substances
- Help individual health boards, Scottish Government and third party groups to improve services and policy

## Scottish Drug Misuse Database (SDMD)

- Established in 1990
- Data collected when individual contacts structured community/residential treatment
- To be replaced by DAISy (combine with waiting times) - only 1 year of DAISy data so far
- Report on SDMD


## Slide title

[PHS homepage](https://publichealthscotland.scot/)

## Slide title

```{r, echo = FALSE}
    kable(table_contents,
          col.names = c("Column heading", "Column heading"),
          format = "markdown")
```
